Constraints on Cosmic Rays, Magnetic Fields, and Dark Matter from Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS and \Fermi

### 2012-02-03 ms.tex
More edits

Gamma-ray-like events are separated from the CR background by imposing selection criteria (cuts) on
the mean-scaled length and width parameters \citep{article:Aharonian_etal:1997,
article:Krawczynski_etal:2006} calculated from a parameterized moment analysis of the shower images
\citep{inproc:Hillas:1985}. The gamma-hadron separation cuts used in this analysis were optimized
{\em a priori} for a weak point source (3\% Crab Nebula flux level) and a differential spectral
index of 2.4, using data taken on the Crab Nebula during the same epoch. Because the VHE gamma-ray
spectrum for the Coma cluster is expected to be a power-law function with an index of about 2.3
\citep{article:PinzkePfrommer:2010}, these cuts are suitable for the analysis of the Coma cluster
data set. It is noted that slightly varying the spectral index
($\pm$ 0.2) does not significantly impact the cuts used for quality selection and gamma-hadron
separation in this work.

@@

\begin{figure*}
\begin{center}
\scalebox{0.45}{\plotone{f1a.eps}}
\scalebox{0.45}{\plotone{f1b.eps}}
\end{center}
\caption{\emph{Left}: Smoothed significance map of the Coma cluster calculated from the observed
excess VHE gamma-ray events over a $4.5^{\circ}\times 4.5^{\circ}$ field of view. The excess counts
were derived using a ring background model \citep{article:Aharonian_etal:2001}. White contours show
the X-ray counts per second in the 0.1 to 2.4 keV energy band from the ROSAT all-sky survey
\citep{article:BrielHenryBohringer:1992}. \emph{Right}: Same as above but with overlaid contours
from GBT radio observations at 1.4 GHz \citep{article:BrownRudnick:2010} where strong point sources
have been subtracted. Shown are also the $0.2^{\circ}$ and $0.4^{\circ}$ radii (dashed cyan)
considered for the extended source analyses presented here.}
\label{fig:skymaps}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\scalebox{0.75}{\plotone{f3.eps}}
\end{center}
\caption{Distribution of significance for Figure \ref{fig:skymaps} and a sampling radius of
$0.2^{\circ}$. The line is a Gaussian fit to the data, with mean close to zero and almost unit
standard deviation.}
\label{fig:sigdist}
\end{figure*}

>>>>

Gamma-ray-like events are separated from the CR background by imposing selection criteria (cuts) on
the mean-scaled length and width parameters \citep{article:Aharonian_etal:1997,
article:Krawczynski_etal:2006} calculated from a parameterized moment analysis of the shower images
\citep{inproc:Hillas:1985}. In this analysis, events with a mean-scaled length in the range 
0.05-1.19 and a mean-scaled width in the range 0.05-1.08 are selected as gamma-ray-like events.
These ranges for the gamma-hadron separation cuts were optimized {\em a priori} for a weak point
source (3\% Crab Nebula flux level) and a differential spectral index of 2.4, using data taken on
the Crab Nebula during the same epoch. Because the VHE gamma-ray spectrum for the Coma cluster is
expected to be a power-law function with an index of about 2.3 \citep{article:PinzkePfrommer:2010},
these cuts are suitable for the analysis of the Coma cluster data set. It is noted that slightly
varying the spectral index ($\pm$ 0.2) does not significantly impact the cuts used for quality
selection and gamma-hadron separation in this work.

@@

\begin{figure*}
\begin{center}
\scalebox{0.45}{\plotone{f1a.eps}}
\scalebox{0.45}{\plotone{f1b.eps}}
\end{center}
\caption{\emph{Left}: Smoothed significance map of the Coma cluster calculated from the excess VHE
gamma-ray events observed with VERITAS over a $4.5^{\circ}\times 4.5^{\circ}$ field of view.
The color scale indicates significance in units of standard deviations. The excess counts were
derived using a ring background model \citep{article:Aharonian_etal:2001}.
White contours show the X-ray counts per second () in the 0.1 to 2.4 keV energy band from the ROSAT
all-sky survey \citep{article:BrielHenryBohringer:1992}. \emph{Right}: Same as above but with
overlaid contours (20-180 mJ in 20 mJ steps) from GBT radio observations at 1.4 GHz \citep{article:BrownRudnick:2010} where
strong point sources have been subtracted. Shown are also the $0.2^{\circ}$ and $0.4^{\circ}$ radii
(dashed cyan) considered for the extended source analyses presented here.}
\label{fig:skymaps}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\scalebox{0.75}{\plotone{f3.eps}}
\end{center}
\caption{Distribution of significances for Figure \ref{fig:skymaps} and a sampling radius of
$0.2^{\circ}$. The line is a Gaussian fit to the data, with mean of -0.11 (close to zero) and
almost unit standard deviation.}
\label{fig:sigdist}
\end{figure*}
